RSA_model2

### 2015-11-14 models/Model_Comparison.Rmd
Model comparison doc - for working through code. Currently copied over from RSA_model2. Had to debug naming issue in exp_data_clean to run run.rsa()

Data
----
```{r}
speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/e8.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/listener.csv")
# priors
# ------
unif = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
empirical = read.csv("~/Desktop/Projects/scalar_implicature//models/prior.csv")
yelp = read.csv("~/Desktop/Projects/scalar_implicature//models/yelp1_priors.csv")
priors = unif
# combine speaker / listener
data <- left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
head(data)
```

@@

Run Model
----------
```{r}
# Run rsa model
# --------------------
run.rsa <- function(d, alpha = 1, useprior = F, usenone = F) {

  mat <- d %>%
    select(stars, degree, speaker.p) %>%
    spread(degree, speaker.p) %>%
    mutate(hi = hi / sum(hi), 
           low = low / sum(low)) %>%
    select(hi, low)

@@

Run model
---------
```{r}
alpha = 5
md <- data %>%
  do(run.rsa(., alpha = alpha, useprior = T, usenone = F))
```

>>>>

Data
----
```{r}
speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
# priors
# ------
unif = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
priors = unif
```

Combine data
```{r}
# Combine speaker / listener
data <- left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
head(data)
```

@@

Run Model
----------
```{r}
# Run rsa model
# --------------------
run.rsa <- function(d, alpha = 1, useprior = F, usenone = F) {
  #d$row = seq(1, nrow(d))
  mat <- d %>%
    select(stars, degree, speaker.p) %>%
    spread(degree, speaker.p) %>%
    mutate(hi = hi / sum(hi), 
           low = low / sum(low)) %>%
    select(hi, low)

@@

Run model
---------
```{r}
alpha = 0
md <- data %>%
  do(run.rsa(., alpha = alpha, useprior = T, usenone = F))
```
